### 2021-04-26 Chapter-3/Chapter-3.tex
Updates from Overleaf

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model. Libgcrypt is a cryptographic library from the GunPG. As some previous work (e.g., CacheD) choose to evaluate their tools on CacheD, we can compare the evaluation results by applying the tool on Libgcrypt.

>>>>

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model. Libgcrypt is a cryptographic library from the GunPG. As some previous work (e.g., CacheD) choose to evaluate their tools on Libgcrypt, we can compare the evaluation results by applying the tool on Libgcrypt.

### 2021-04-26 Chapter-5/Chapter-5.tex
Update Chapter-5.tex
Updates from Overleaf

\chapter{Precise Analysis on Multiple-trace Attacks}\label{chapter5}
\section{Introduction}
Side-channel attacks allow attackers to infer sensitive information based on the non-functional behaviors of the computer system. Examples of those non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}. In summary, if the program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing those secret-dependent behaviors. While separate side-channel attacks may have different forms and patterns, we find a large portion of them share the same fundamental reasons. That is, the memory access pattern is dependent on the original sensitive input.

@@

\textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcropt, and wolfSSL. Encryption ciphers can be divided into three categories:  symmetric ciphers and asymmetric ciphers. For stream ciphers, we use RC4. For symmetric ciphers, we choose AES. We also evaluate the tool on RSA, a widely used algorithm in the public-key cryptosystem.

>>>>

\chapter{Precise Analysis on Multiple-trace Attacks}\label{chapter5}
\section{Introduction}
Side-channel attacks allow attackers to infer sensitive information based on the non-functional behaviors of the computer system. Examples of these non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}. In summary, if the program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing those secret-dependent behaviors. While separate side-channel attacks may have different forms and patterns, we find that a large portion of them share the same fundamental reasons. That is, the memory access pattern is dependent on the original sensitive input.

@@

\textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcrypt, and wolfSSL. Encryption ciphers can be divided into three categories:  symmetric ciphers and asymmetric ciphers. For stream ciphers, we use RC4. For symmetric ciphers, we choose AES. We also evaluate the tool on RSA, a widely used algorithm in the public-key cryptosystem.
